STAT0030_ICA2

### 2019-02-18 STAT0030_ICA2/STAT0030_ICA2.Rmd
Hongwei
vision  2 question 1 c

---
title: "STAT0030_ICA2"
author: "Hongwei Peng"
date: "10/02/2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

@@

```{R question_1_c}
boxplot(mpg~tr, #MPG by TR
        data=rawdata, #set the dataset
        xlab="Gear Transmission Type" , #add the xlab title
        ylab="Miles Per Gallon", #add the ylab title
        main="MPG by Gear Transmission Type", #add the main title
        names=c("Automatic","Manual")) #change xlab value to character
t.test(mpg~tr, data=logdata)
model<-lm(mpg~tr+hp+wt, data=logdata); # i.e, full without qsec and gears
summary(model)
summary(model$residuals)
par(mfrow=c(2,2))
plot(model)

best<-step(model, direction="both")
summary(best)
summary(best$residuals)
par(mfrow=c(2,2))
plot(best)

>>>>

---
title: "STAT0030_ICA2"
author: "Hongwei Peng"
date: "10/02/2019"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---

@@

```{R question_1_c}
boxplot(mpg~tr, #MPG by TR
        data=rawdata, #set the dataset
        xlab="Gear Transmission Type" , #add the xlab title
        ylab="Miles Per Gallon", #add the ylab title
        main="MPG by Gear Transmission Type", #add the main title
        names=c("Automatic","Manual")) #change xlab value to character
t.test(mpg~tr, data=logdata)
model<-lm(mpg~tr+hp+wt, data=logdata); # i.e, full without qsec and gears
summary(model)
summary(model$residuals)
par(mfrow=c(2,2)) #put 4 graphes together
plot(model) #plot 4 graphes as following

best<-step(model, direction="both")
summary(best)
summary(best$residuals)
par(mfrow=c(2,2)) #put 4 graphes together
plot(best)#plot 4 graphes as following
